\documentclass[12pt]{article}
%\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}

\title{8th Grade Chapter 1 and 2 Test}
\date{October 7, 2025}

\begin{document}

\maketitle

\textbf{Instructions:} Show all your work clearly. Work in your composition notebook. Good luck!

\begin{enumerate}
    \item \textbf{Scientific Notation}
    \begin{enumerate}
        \item Write $3,400,000$ in scientific notation.
        \item Write $0.000045$ in scientific notation.
        \item Write $2.5 \times 10^4$ in standard form.
        \item Write $7.8 \times 10^{-3}$ in standard form.
        \item Evaluate: $(3 \times 10^2)(4 \times 10^5)$. Write your answer in scientific notation.
    \end{enumerate}

    \item \textbf{Significant Digits}
    \begin{enumerate}
        \item How many significant digits are in $0.00340$?
        \item How many significant digits are in $1,200$?
        \item How many significant digits are in $0.0500$?
        \item Round $3.4567$ to 3 significant digits.
        \item Round $0.001234$ to 2 significant digits.
    \end{enumerate}


    \item \textbf{Estimation and Irrational Numbers}
    \begin{enumerate}
        \item Estimate $\sqrt{50}$ to the nearest whole number.
        \item Between which two consecutive integers does $\sqrt{75}$ lie?
        \item Is $\sqrt{64}$ rational or irrational? Explain.
    \end{enumerate}

    \vspace{1in}

    \item \textbf{Linear Equations}
    \begin{enumerate}
        \item Solve for $x$: $3x + 7 = 22$
        \item Solve for $x$: $\frac{x}{3} + 2 = 8$
        \item Solve for $x$: $4(x - 2) = 3x + 5$
    \end{enumerate}

    \item \textbf{Systems of Equations - Graphical Method}
    \begin{enumerate}
        \item Graph the system and find the solution:
        \begin{align*}
        y &= 2x + 1 \\
        y &= -x + 4
        \end{align*}
        \item What is the solution to the system above?
    \end{enumerate}

    \item \textbf{Systems of Equations - Substitution Method} \newline Solve using substitution:
        \begin{align*}
        x + y &= 7 \\
        2x - y &= 2
        \end{align*}

    \item \textbf{Systems of Equations - Elimination Method}
    \begin{enumerate}
        \item Solve using elimination:
        \begin{align*}
        3x + 2y &= -5 \\
        -3x - 3y &= 124
        \end{align*}
        \item Check your answer by substituting back into both equations.
    \end{enumerate}

    \item \textbf{Applications of Systems} Two numbers have a sum of 125 and a difference of 17.  Find the two numbers.

    \item \textbf{Extra Credit} Solve the following system of equations using any method you choose:
    \begin{align*}
    2x + 3y &= 55 \\
    3x - 2y &= -15
    \end{align*}
\end{enumerate}

\end{document}
